---
title: "Data Visualization"
author: "KiseokUchicago"
date: "2020-09-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Data visualization lecture
Peter Carbonetto

In this lesson, you will use ggplot2 to create effective visualizations of data. The ggplot2 package
is a powerful plotting interface that extends the base plotting functions in R. You will learn that
creating effective visualizations hinges on good data preparation. (In reality, good data preparation
can take days or weeks, but we can still illustrate some useful data preparation practices.)
The main difference with Advanced Computing 1 is that we take a more in-depth look at ggplot2
and plotting strategies.

```{r knitr-options, echo=FALSE}
knitr::opts_chunk$set(results = "hide",collapse = TRUE,
                      fig.height = 3,fig.width = 3,fig.align = "center")
```

### Install libraries
```{r}
# install.packages("ggplot2")
# install.packages("cowplot")
# install.packages("ggrepel")
# install.packages("htmlwidgets")
# install.packages("plotly")
library(ggplot2)
library(cowplot)
library(ggrepel)
library(htmlwidgets)
library(plotly)

```

# Exercize 1: Do smaller dogs live longer?

## Import and explore the data
```{r}
# Import data
dogs <- read.csv("data/dogs.csv",stringsAsFactors = FALSE)
head(dogs)
colnames(dogs)
summary(dogs)
str(dogs)

# Let’s take a closer look at the shortcoat column:
unique(dogs$shortcoat)
mean(dogs$shortcoat)
mean(dogs$shortcoat, na.rm=TRUE)
```



