---
title: "Data Visualization"
author: "KiseokUchicago"
date: "2020-09-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Data visualization lecture
Peter Carbonetto

In this lesson, you will use ggplot2 to create effective visualizations of data. The ggplot2 package
is a powerful plotting interface that extends the base plotting functions in R. You will learn that
creating effective visualizations hinges on good data preparation. (In reality, good data preparation
can take days or weeks, but we can still illustrate some useful data preparation practices.)
The main difference with Advanced Computing 1 is that we take a more in-depth look at ggplot2
and plotting strategies.

Use this site for reference

https://ggplot2.tidyverse.org/reference/

```{r knitr-options, echo=FALSE}
knitr::opts_chunk$set(results = "hide",collapse = TRUE,fig.align = "center")
```

### Install libraries
```{r}
# install.packages("ggplot2")
# install.packages("cowplot")
# install.packages("ggrepel")
# install.packages("htmlwidgets")
# install.packages("plotly")
library(ggplot2)
library(cowplot)
library(ggrepel)
library(htmlwidgets)
library(plotly)

```

# Exercize 1: Do smaller dogs live longer?

## Import and explore the data
```{r}
# Import data
dogs <- read.csv("data/dogs.csv",stringsAsFactors = FALSE)
head(dogs)
colnames(dogs)
summary(dogs)
str(dogs)

# Let’s take a closer look at the shortcoat column:
unique(dogs$shortcoat)
mean(dogs$shortcoat)
mean(dogs$shortcoat, na.rm=TRUE)
```

## Plotting
```{r}
# basic function
plot(dogs$weight,dogs$aod)

# use ggplot2
p1 <- ggplot(dogs,aes_string(x = "weight",y = "aod")) +
  geom_point()
p1
# some improvements
library(cowplot)
p2 <- p1 + labs(x= 'body weight (lbs)', y= 'longevity (years)', title = "Bigger dogs live less") + theme_cowplot()
p2

# Surprising subtlety with colour.
p4 <- ggplot(dogs,aes_string(x = "weight",y = "aod", color = 'shortcoat')) + geom_point() + theme_cowplot()

p4

# fix the plot to discrete value
class(dogs$shortcoat)
dogs$shortcoat <- factor(dogs$shortcoat)
summary(dogs$shortcoat)

p4 <- ggplot(dogs,aes_string(x = "weight",y = "aod", color = 'shortcoat')) + geom_point() + theme_cowplot()

# voila!
p4

```
## Add linear regression 
use colors() to see the list of colors
```{r}
fit <- lm(aod ~ weight,data=dogs)
summary(fit)
coef(fit)

# compare the fit
p5 <- p4 + geom_abline(color='forestgreen', intercept = coef(fit)[1], slope=coef(fit)[2]) + geom_abline(intercept = 13, slope = -1/28, color = 'orange')

p5

# add breed names
library(ggrepel)
p6 <- p5 + geom_text_repel(mapping =aes_string(label = 'breed'), color = 'darkblue')

p6

# add only fraction of them
p6 <- p5 + geom_text_repel(mapping =aes_string(label = 'breed'), color = 'darkblue', data=dogs[1:20,])

p6

# Save the image to pdf
# ggsave('scatter_plot.pdf',p6)

```

## Bonus: Install a newer version of ggrepel
```{r}
# devtools::install_github('slowkow/ggrepel')
# failed to install the newer version

```



